Reply to Reviewer #2

### 2022-02-05 GitControlled/Writing/Re_JournalSubmission/replies_rev_2.rmd
Large revise of the manuscript and codes for re-submission

---
title: "Reply to Reviewer #2"
author: 
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

@@

+ I modified the titles of all tables and figures.
</span>

@@

+ I included units in Table 1 and Fig. 3. 
</span>

@@

+ I added indent between "(kg/ha)" and "of"(before: "RMSE (kg/ha)of EONR", after: RMSE (kg/ha) of EONR)
</span>

@@

+ I added the unit (kg/ha) in the title of Table 3. Similarly, I added units in Table 2, Figure 8, 9, 10, and 11.  
</span>

>>>>

---
title: "Reply to Reviewer #2"
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

@@

+ I modified all the titles of tables and figures.
</span>

@@

+ I removed Table 1. Instead, I explained about those parameters in section 3.1.3. I added units of "ymax" and "$\varepsilon$" to Figure 3.
</span>

@@

+ I corrected the typo. 
</span>

@@

+ I added the unit (kg/ha) to the Table: Mean RMSE of Yield Prediction by ML Methods and Modeling Scenarios. Similarly, I provided units to other result tables.
</span>
